|

### 2019-08-30 manuscript/manuscript.Rmd

# Property and Casualty Ratemaking

@@

# Interpretability in the Ratemaking Context

@@

# Applying Model Interpretation Techniques

@@

# Conclusion

>>>>

The rest of this paper is organized as follows: Section \ref{ratemaking} provides an overview of P&C ratemaking, Section \ref{interpretability} discusses model interpretability in the context of ratemaking and proposes specific tasks for model explanation, Section \ref{application} describes current model interpretation techniques and applies them to the tasks defined in the previous section, and Section \ref{conclusion} concludes.

# Property and Casualty Ratemaking {#ratemaking}

@@

# Interpretability in the Ratemaking Context {#interpretability}

@@

# Applying Model Interpretation Techniques {#application}

@@

# Conclusion {#conclusion}
